%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[line,margin,9pt]{res} 
\newsectionwidth{1in}
\topmargin= -0.8in
%\bottommargin= 0in
\oddsidemargin -.5in
\evensidemargin -.75in
\textheight 10.375in
\textwidth=6.5in
%\resumewidth=5in
\itemsep=0in
\parsep=0in


%\usepackage[legalpaper, margin=0.5in]{geometry}
% margin = 1in

% Default font is the helvetica postscript font
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
% Increase text height
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage[utf8]{inputenc}
\usepackage{dirtytalk}

%\textheight=700pt

\begin{document}
%\newsectionwidth{0.71in}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{\centering{Tyler Andrew Cultice\noindent\hbox to 0.15\textwidth{} tylercultice@gmail.com\noindent\hbox to 0.175\textwidth{} (937)631-9267}}


\address{\href{https://www.linkedin.com/in/tyler-cultice-43265520b/}{\textbf{[LinkedIn]}} \\
\href{https://github.com/tcultice21}{\textbf{[Github]}} \\
\href{https://scholar.google.com/citations?hl=en\&user=9eUFpBwAAAAJ}{\textbf{[Google Scholar]}} %\quad \href{https://sites.google.com/view/md-saif-hassan/}{\textbf{[Personal Site]}
\noindent\hbox to 0.75\textwidth{}}\hfil

% \href{https://www.researchgate.net/scientific-contributions/Tyler-Cultice-2178791037}{\textbf{[Researchgate]}}

\begin{resume}
\vspace{-10mm}

\section{EDUCATION}
\begin{itemize}
\item \bf{University of Tennessee, Knoxville}, TN-37916, USA\\
\bf GPA 4.00/4.00 \hfill \sl PhD in Computer Engineering\\
\textbf {2021--July 2025}

\item \bf{University of Kentucky}, Lexington, KY-40506, USA\\
\bf GPA 3.879/4.00 \hfill \sl Bachelor of Science in Computer Engineering\\
\textbf {2017--2021}

% \item \bf{Shahid Syed Nazrul Islam College}, Mymensingh-2201, BD\\
% \sl Higher Secondary-School Certificate in Science\\
% \sl GPA \bf 5.00/5.00\\
% \textbf {2013-2015}\\
% \sl Graduation: \bf August,2015.


\end{itemize}

%\section{RESEARCH\\INTERESTS}
%\begin{itemize}
%\item \bf Cybersecurity, 
%\bf Cyberphysical Systems, 
%\bf Firmware Design, 
%\bf Embedded Systems, 
%\bf FPGAs,
%\bf Post-Quantum Cybersecurity, 
%\bf Additive Manufacturing, 
%\bf Quantum Anomaly Detection, 
%\bf Quantum Machine Learning
%\end{itemize}


\section{ENGINEERING\\SKILLS\\\textbf{[Level: Advanced]}}
\begin{itemize}
\item \textbf{Programming Languages:} Python, Embedded C, C, C++, C\#, Rust, Verilog/SystemVerilog, VHDL, Java, Matlab  ARM/x86 Assembly. \\
\textbf{Architectures/Applications:} RTOS, Cryptography, FPGA Design and Synthesis, OOP, CUDA, RISC-V, ARM, RTL Design/Verification, Linux Kernel, CAN, UART, Multi-core computing. \\
\textbf{Machine Learning \& Quantum Libraries:} Keras, Pytorch, Tensorflow, IBM Qiskit, Pennylane.\\
%\textbf{Security Tools:} NMAP, Metasploit, SQLMap, Netcat. \\ 
\textbf{Design/Other Tools:} Virtuoso, Xilinx Vivado, Keil µVision, Intel Quartus, Git, GDB. \\
\textbf{Operating System:} Windows, Linux (Unix).
\end{itemize}
%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
% \vspace{.4cm}
% \section{RESEARCH \\ BACKGROUND}
% \begin{itemize}


% \item \textbf{BSc thesis: LULC classification by semantic segmentation of satellite images using FastFCN .}\\
% Supervisor: Dr. A. K. M. Nazrul Islam, Professor, MIST

% \item \textbf{Smart Wheelchair with Medical Sensors and Voice Controlled Navigation: } Worked on this project in a group of 5.It has voice controlled module, temperature sensor, Ultrasonic sensor and GSM module.

% \item \textbf{Doc Scanner for windows PC: }Creates PDF out of pictures. Faster than mobile device. Used computer vision module and is written in python.

% \item \textbf{Satellite Image Segmentation: }Used the Pytorch module to reproduce FastFCN and introduced a grid block to efficiently segment high resolution satellite images.

% \item \textbf{Road Sign Recognizer using open-cv: }Trained a dataset of road signs in a VGG16 architecture.Used it to test various road signs which can help to improve the self driven vehicles.

% \item \textbf{License plate recognition: }Used the YOLO v4 for license plate localization and Tessaract V5 for character recognition

% \item \textbf{Automatic DG placement with the help of Machine learning: }Used KNN for forecasting and predicting bus voltage and line loss to decide on new DG placement.
% \clearpage

% \item \textbf{Automatic OMR detection Using Image Processing: }Detects marked answers and evaluate it in OMR using computer vision. Updates the grades according to the detection algorithm.

% \item \textbf{Bangla Character Recognition with custom CNN: }It could recognise handwritten and printed bangla characters with more than 93\% accuracy. Trained with open-source bangla character datasets on custom made CNN.

% \item \textbf{Eight bit PC with Assembly Language: }It could perform 10 basic commands and was Designed in Proteus and operated by Assembly language.

% \item \textbf{Modelling Non-Verbal Communications for physically challenged:}(Ongoing)


% \end{itemize}

\section{EXPERIENCE}
\begin{itemize}
\item \textbf{NSF Graduate Research Fellow}, Dept of EECS, University of Tennessee, Knoxville (2022-Present)
\item Teaching Assistant, Dept of EECS, University of Tennessee, Knoxville (2021-Present)
\item Undergraduate Research Assistant, Dept of ECE, University of Kentucky, Lexington (2019-2021)

\end{itemize}

\section{DISTINCTIONS AND AWARDS}
\begin{itemize}
\item \textbf{2022--Present - NSF Graduate Research Fellowship Program (GRFP):} \\
Prestigious fellowship awarded to outstanding students with significant contributions to STEM.
\item \textbf{2025 - UTK Gonzalez Outstanding Graduate Teaching Assistant Award: } \\
Award for outstanding commitment, dedication, and notable ambition in EECS academic pursuits.
\item \textbf{2021 - Upsilon Pi Epsilon (UPE) Award:} \\
IEEE Computer Society Award for Academic Success in Computer Engineering.
\item \textbf{2020 - Schneider Electric Fellowship, University of Kentucky:} \\
Smart-Home Research on ML-based CPS Anomaly Detection in collaboration with SPARK Lab.

\end{itemize}

\section{RELEVANT PROJECTS}
\begin{itemize}

\item \textbf{Crystals-KYBER-based Post-Quantum Cryptographic 3D Printing Security - \\
	\small{HOST 2024 Hardware Demonstration with UTK SEAMTN}}
\begin{itemize}
\item Developed a Crystals-KYBER \textbf{post-quantum cryptographic framework in embedded C} for 3D Printer in collaboration with Southeastern Advanced Machine Tools Network (SEAMTN).
\item Engineered a novel \& highly efficient \textbf{CAN communication} tree/graph structure for 3D printers with colleague Joseph Clark.
\item Built a proof-of-concept 3D printer farm, presented as hardware demo at security conference HOST 2024, with \textbf{simple API callback structure for plug-and-play}.
\item Taught prospective engineers offensive/defensive security for manufacturing networks with Kali.
\end{itemize}

\item \textbf{Post-Quantum Cryptographic Vehicular Security Framework - \\
	\small{UTK/DoD-funded Dissertation Research}} 
\begin{itemize}
\item Developed an \textbf{embedded CAN framework in C} that is safe from quantum threats for commercial vehicles while adhering to original ISO 11898 protocol specifications.
\item Built embedded testbench with Physically Unclonable Functions for collecting performance benchmarks.
\end{itemize}

\item \textbf{Smart-Home Sensor Anomaly Detection using Keras Deep Learning - \\
	\small{Research Collaboration with Schneider Electric fellowship}}  
\begin{itemize}
\item Proposed a \textbf{ML model} to identify sensor anomalies in Honda US Smart Home data.
\item Trained deep learning \textbf{neural network model in Python} in collaboration w/ Schneider Electric.
\end{itemize}

\item \textbf{ASHRAE-based Smart Home COMFORT Controller - \\
	\small{UKY Senior Project, Best CAPSTONE Award 2021}}
\begin{itemize}
\item Designed Smart HVAC with the UKY Spark Lab to meet ASHRAE ``COMFORT" Standards.
\item Lead small team to develop a lightweight, \textbf{secure communication firmware/API with embedded C, C++, and C\#} for WLAN-based, smart integration for HVAC devices.
\item Documented various performance and functionality metrics for future use in Spark Lab.
\end{itemize}

\item \textbf{GUI Operating System Designed for RISC-V Architecture - \\
	\small{Graduate Classwork in Adv. Operating System Design}} 
\begin{itemize}
\item Designed an \textbf{operating system and SBI in C} for a virtual \textbf{RISC-V} with GUI/input support.
\item Implemented supervisor, hypervisor, and user modes for privilege protection.
\item Utilizes \textbf{``hardware threading"} for a multi-core RISC-V ISA with power saving capabilities.
\end{itemize}

\item \textbf{Quantum Anomaly Detection for Industrial Control Systems - \\
	\small{Collaborative Research with Oak Ridge National Lab (ORNL)}}  
\begin{itemize}
\item Engineered high-accuracy \textbf{Quantum ML models in Python} for detecting cyberattacks in critical infrastructures with Oak Ridge National Lab (ORNL).
\item Determined metrics for parametrizing the success, or advantage, of a CPS-related QSVM model on detecting real-world industrial cyberattacks.
\item Investigated the effects of modern NISQ noise in \textbf{quantum machine learning}.
\item Designed Python framework for easy integration of IBM Qiskit in Cyberphysical Systems.
\end{itemize}

\item \textbf{FPGA-Based Multilayer Perceptron (MLP) as a Neural Network using Verilog - \\
	\small{Personal Research Project alongside Md. Saif Hassan Onim}} 
\begin{itemize}
\item Designed a \textbf{MLP neural network accelerator in SystemVerilog} with parametrizable neurons and layers using dedicated DSP hardware on the Intel Cyclone V and Xilinx Artix-7.
\item Implemented \textbf{wrapper/controller} for easy interfacing with SoC RAM and I/O.
\item Evaluated various performance metrics of the FPGA design in terms of power, area, and timing.
\end{itemize}

%\item \textbf{16-bit Pipelined Processor for 8-bit SIMD Posit Arithmetic in Verilog (Gr8BOnd) - \\
%	\small{UKY Classwork in Adv. Computer Architecture Design}} 
%\begin{itemize}
%\item Implemented a 16-bit pipelined processor capable of performing SIMD Within a Register (SWAR) in a Turing-complete instruction set.
%\item Fully developed \textbf{in Verilog and implemented on the Intel Cyclone V SoC/FPGA}.
%\item Developed a Monte Carlo-based testing apparatus for validating processor functionality via Icarus.
%\end{itemize}

%\item \textbf{FPGA Implementation and Side-Channel Analysis of PRESENT \& AES Cryptography - \\
%	\small{Research Project for Developing New UTK Hardware Security Course}}  
%\begin{itemize}
%\item Designed FPGA implementation of the PRESENT \& AES cryptographic engines with a state machine-based controller in Verilog.
%\item Taught students how to perform validation and investigate power usage, timing, and utilization.
%\item Performed side-channel power analysis attacks on HW implementations of PRESENT \& AES.
%\end{itemize}

\end{itemize}

\section{MAJOR\\ACADEMIC\\COURSES}
\begin{itemize}
\item \bf Systems Programming,
\bf Computer Programming,
\bf Network/Software/Embedded Security,
\bf System on Chip Design,
\bf Machine Learning,
\bf Compiler Design,
\bf Adv. Operating System Design,
\bf Emerging Computing/Quantum,
\bf GPU \& Multicore Programming,
\bf Data Mining and Analytics,
\bf Adv. Embedded Systems,
\bf Algorithm Design/Analysis,
\bf Digital Logic Design
\end{itemize}

\section{PUBLICATIONS}
\begin{itemize}

\item\textbf{Tyler Cultice}, Md. Saif Hassan Onim, Annarita Giani and Himanshu Thapliyal, \say{Anomaly Detection for Real-World Cyber-Physical Security using Quantum Hybrid Support Vector Machine}, \textit{Proceedings of IEEE Computer Society Annual Symposium on VLSI 2024 (ISVLSI 2024), Knoxville, TN, USA, July 1-3, \textbf{2024 (Best Paper Award)}}

\item \textbf{Tyler Cultice}, Joseph Clark, Himanshu Thapliyal. ``A Novel Hierarchical Security Solution for Controller-Area-Network-Based 3D Printing in a Post-Quantum World." Sensors 23.24 \textbf{(2023)}: 9886.

\item \textbf{Tyler Cultice}, Joseph Clark, and Himanshu Thapliyal. ``Lightweight Hierarchical Root-of-Trust Framework for CAN-Based 3D Printing Security." Proceedings of the Great Lakes Symposium on VLSI 2023. \textbf{2023}.

\item \textbf{Tyler Cultice}, and Himanshu Thapliyal. ``Vulnerabilities and Attacks on CAN-Based 3D Printing/Additive Manufacturing." IEEE Consumer Electronics Magazine 13.1 \textbf{(2023)}: 54-61.

\item Chin, Jun-Cheng, Himanshu Thapliyal, and \textbf{Tyler Cultice}. ``CAN Bus: The Future of Additive Manufacturing (3D Printing)." IEEE Consumer Electronics Magazine \textbf{(2022)}.

\item \textbf{Tyler Cultice}, and Himanshu Thapliyal. ``PUF-based post-quantum CAN-FD framework for vehicular security." Information 13.8 \textbf{(2022)}: 382.

\item \textbf{Tyler Cultice}, Dan Ionel, and Himanshu Thapliyal. ``Smart home sensor anomaly detection using convolutional autoencoder neural network." 2020 IEEE International Symposium on Smart Electronic Systems (iSES)(Formerly iNiS). IEEE, \textbf{2020}.

\item \textbf{Tyler Cultice}, Carson Labrado, and Himanshu Thapliyal. ``A puf based can security framework." 2020 IEEE Computer Society Annual Symposium on VLSI (ISVLSI). IEEE, \textbf{2020}.

\end{itemize}
%\section{TEACHING \\ EXPERIENCE}

%\section{DISTINCTIONS AND AWARDS}
%\begin{itemize}
%\item \textbf{2020 - Schneider Electric Fellowship, University of Kentucky:} \\
%Smart-Home Research on Machine-Learning-based CPS Anomaly Detection in collaboration with Dr. Dan Ionel from UKY.
%\item \textbf{2021: Upsilon Pi Epsilon (UPE) Award:} \\
%IEEE Computer Society Award for Academic Success in Computer Engineering.
%\item \textbf{2022-Present - NSF Graduate Research Fellowship Program (GRFP):} \\
%Prestigious fellowship awarded to outstanding graduate students with significant contributions to STEM.
%\item \textbf{2021-present:} Graduate Student Member, Institute of Electrical and Electronics Engineers (IEEE).
%\item \textbf{2023-present:} Member, Association for Computing Machinery (ACM).
%\item \textbf{2023:} Web Chair, GLSVLSI'23
%\item \textbf{2024:} Registration and Web Chair, ISVLSI'24
%\item \textbf{Reviewer:} DAC, GLSVLSI, ISVLSI

%\end{itemize}
\end{resume}
\end{document}